---
title: "Visualize Data"
output: html_notebook
---

### Your Turn 5: The ggplot template and aesthetics

For this exercise, we will practice a technique called "pair programming". One person in the breakout room will share their screen, showing the RStudio Cloud console. This person will act as the "scribe" for the rest of the group who will contribute by making suggestions. 

Run the following code chunk to set up the practice data sets.

```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(lubridate)

covid_testing <- read_csv("covid_testing.csv") 
```



Let's recreate the histogram of *pan_day*. 

You will need to:

1. Pick a data set: *covid_testing*
2. Choose a geom function: *geom_histogram()*
3. Map aesthetic properties of the graph to variables of the data frame (in this case, the *pan_day* variable should be on the x axis).

Fill in the blanks and run the code to create the plot.

(Hint: if you get stuck, take a look at the slide titled "ggplot()"!)

```{r}
ggplot(data = ______) +
  ______(mapping = aes(x = ______))
```




When you run this code, you will most likely have what looks like an error displayed above the graph:

  `stat_bin()` using `bins = 30`. Pick better value with `binwidth`.

This is actually just a message from R, telling you that it's a bad idea to use a default bin width. 

The *pan_day* variable holds the day of the pandemic (an arbitrary day in late February of 2020) on which the COVID test order was placed. What would be an appropriate binwidth for *pan_day*? Discuss with your breakout-roommates! 

(Hint: you might want to be able to see _daily_ COVID test volumes!)

Now fill in the blanks below to recreate the code from the previous chunk, with the *binwidth* argument passed to the *geom_histogram* function. 

```{r}
ggplot(______) +
  ______(mapping = aes(______), binwidth = ______)
```




The effect of reducing the bin width (and increasing the number of bins) is that the data is now presented in much greater detail. 

Let's next add some color!

Copy and paste the previous code chunk and add an aesthetic mapping that maps the *fill* aesthetic to the *result* column. (Hint: all aesthetics must be defined inside the aes() function!)




Stop here.

*******************************************************





### Your Turn 6: Geom functions

Let's do another pair programming exercise! (Someone else should be the scribe this time.)

Run the following code chunk:

```{r}
ggplot(data = covid_testing) +
  geom_histogram(mapping = aes(x = pan_day))
```


Now, with your group, try to figure out how you would modify the code above so it draws a frequency polygon instead of histogram. Hint: Google is your friend!

```{r}

```




Modify the previous code chunk so that the frequency polygon's line color is blue. (Hint: color values go in quotes!)

```{r}

```







Within your group, predict what the following code will do. 

Then run it.

```{r}
ggplot(data = covid_testing) +
  geom_histogram(mapping = aes(x = pan_day)) +
  geom_freqpoly(mapping = aes(x = pan_day))
```

